\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineer}
    {InterCloud}
    {Paris, France}
    {Oct. 2016 - Present}
    {
      \begin{cvitems}
        \item {Building API \& Portal to provision connectivity services to Cloud Service Providers as AWS, Azure, GCP, OVH ...}
         \item {Design \& Implemented a high availability, distributed \& fault tolerant system to monitor PoP (Latency, Jitter, Packets Loss, Availability).}
         \item {Presented training sessions about CI/CD \& Kubernetes}
      \end{cvitems}
    }
    \cventry
    {Software Engineer Intern}
    {Capgemini}
    {Bordeaux, France}
    {Apr. 2016 - Sept. 2016}
    {
      \begin{cvitems}
        \item {Developed front-end and back-end of CCVRP's web service.}
         \item {Implemented IoT (Internt of Things) Healthcare application for Hacking Health Camps (AquitHealth, Bordeaux I/O, VivaTech).}
         \item {Provided training sessions about Continuous Integration with Docker for a group of Software Engineers.}
         \item {Developed an Android application to visualize resumes for Pôle Emploi Department.}
      \end{cvitems}
    }
    \cventry
    {Software Engineer Intern}
    {Capgemini}
    {Bordeaux, France}
    {Jun. 2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Developed features and components for CCVRP's corporate website, to serve fast pages to more than 2 million unique visitors per year.}
         \item {Being part of the first team in France to run Docker in production.}
         \item {Developed Spring and Android app at the Innovation Department of Capgemini.}
      \end{cvitems}
    }
    \cventry
    {Software Engineer Intern}
    {CNESTEN (National Center for Enery Sciences and Nuclear Techniques)}
    {Rabat, Morocco}
    {Feb. 2014 - Jul. 2014}
    {
      \begin{cvitems}
        \item {Developed cross-platform application to help researchers in solving complex atom equations using Monte Carlo method.}
      \end{cvitems}
    }
\end{cventries}
